---
title: "week4_part1"
author: "Caitie Reza"
date: "11/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence Intervals


```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)
t.test(otter_length)

```

## T-test (1-sample t-test)

See a claim: mean otter length is 50 inches

Use your data to test that claim.  

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test


```

### P Value

We tested the claim that mean otter length is 50 inches and got a p-value of .0444:

If the population mean really is 50 inches, then there's a 4.444% chance that we could have randomly taken a sample from our population that has a mean that is at LEAST as different from 50 as my sample mean



## Two sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)

```

### Wut dis mean

Null hypothesis: Difference in means is equal to 0

P Value = .8849.  If these samples are drawn from populations with the same mean (null hypothesis), there's an 88.5% chance that additional samples taken from those two populations will be at LEAST as different as these samples. 




